---
title: "Dreaded homework"
author: "Jocelyn Hafer"
date: "November 9, 2015"
output: html_document
---


####Initialize packages from library.
```{r, message=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(RCurl)
```

####From movies dataset, pull movie title, imdb rating percentiles, genre
#####Tidy data by rating frequency
#####Tidy data by genre
```{r}
movie_select <- select(movies, title, r1:r10, Action:Short)

movie_rating <- select(movie_select, title, r1:r10)
movie2 <- movie_rating %>% gather(rating, frequency, r1:r10) %>% arrange(title)

movie_genre <- select(movie_select, title, Action:Short)
movie3 <- movie_genre %>% gather(genre, frequency, Action:Short) %>% arrange(title) %>% filter(frequency == 1)
```

####From cafe data:
```{r}
url <- getURL("https://raw.githubusercontent.com/shv38339/statcomp597d/master/cafedata.csv")
dat2 <- read.csv(file = textConnection(url), header = TRUE)
```

#####I would tidy the data by collapsing the dates into just days of the week and looking at items sold and wasted by day of the week.

#####Data could be untidied by un-arranging it from date order and lumping together the month/day/year with the day of the week.
```{r}
untidy <- dat2 %>% arrange(Bread.Sand.Sold, Bread.Sand.Waste, Wraps.Sold, Wraps.Waste, Muffins.Sold, Muffins.Waste)
untidy$untidy2 <- paste(untidy$Date, untidy$Day.of.Week, sep = " ")
```
